Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-10-06 paper/author_disambiguaton.tex
add a missing space

The remainder of this report is structured as follows. In Section~\ref{related-works},
we briefly review machine learning solutions for author disambiguation.
The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}.Experiments
are carried out in Section~\ref{experiments}, where we explore and validate
features for the supervised learning of a linkage function and compare
strategies for the semi-supervised clustering of publications.
Finally, conclusions and future works are discussed in Section~\ref{conclusions}.

>>>>

The remainder of this report is structured as follows. In Section~\ref{related-works},
we briefly review machine learning solutions for author disambiguation.
The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}. Experiments
are carried out in Section~\ref{experiments}, where we explore and validate
features for the supervised learning of a linkage function and compare
strategies for the semi-supervised clustering of publications.
Finally, conclusions and future works are discussed in Section~\ref{conclusions}.
